Figures

### 2020-03-02 figures/07_model-selection.Rmd
use hu4 ids in re plot and order by longitude

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(global_offset)) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TP") + xlab("Zone ID") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

```{r tn_re, fig.width=3.25, fig.height=4.5}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
global_offset <- dplyr::filter(re_global, 
                               response == "tn", 
                               term == get_re_text(
                                 as.character(fit_tn$formula)))["50%"]
fit_tn$re <- fit_tn$re %>%
  mutate_at(vars(matches("%")), function(x) x + as.numeric(global_offset))

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_hline(yintercept = as.numeric(global_offset)) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN") + xlab("Zone ID") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  labs(fill = "LULC Sensitive", color = "LULC Sensitive") +
  cowplot::theme_cowplot() +
  theme(legend.position = c(0.7, 0.8)) +
  theme(rect = element_rect(fill = "transparent"), 
        strip.background = element_rect(fill = "transparent"), 
        strip.text = element_blank()) +
  facet_wrap(~pretty) +
  # xlim(c(0, 34)) + 
  xlab("Clay (percent)")

@@

```{r re}
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0,0,0), "cm")), 
                   rel_widths = c(1, 0.9)), 
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")),
ncol = 1, rel_heights = c(1, 0.05))

>>>>

hu4_key <- dplyr::select(st_drop_geometry(hu4), HUC4, ZoneID, Lon) %>%
  mutate(hu4vzoneid = gsub("HU4_", "", ZoneID))
fit_tp$re <- left_join(fit_tp$re, hu4_key, by = "hu4vzoneid") %>%
  arrange(desc(Lon))
fit_tp$re$HUC4 <- factor(fit_tp$re$HUC4, levels = fit_tp$re$HUC4)

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = HUC4, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(global_offset)) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TP") + xlab("HUC4 ID") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

```{r tn_re, fig.width=3.25, fig.height=4.5}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
global_offset <- dplyr::filter(re_global, 
                               response == "tn", 
                               term == get_re_text(
                                 as.character(fit_tn$formula)))["50%"]
fit_tn$re <- fit_tn$re %>%
  mutate_at(vars(matches("%")), function(x) x + as.numeric(global_offset))
fit_tn$re <- left_join(fit_tn$re, hu4_key, by = "hu4vzoneid") %>%
  arrange(desc(Lon))
fit_tn$re$HUC4 <- factor(fit_tn$re$HUC4, levels = fit_tn$re$HUC4)

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_hline(yintercept = as.numeric(global_offset)) +
  geom_pointrange(aes(x = HUC4, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN") + xlab("HUC4 ID") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  labs(fill = "LULC Sensitive", color = "LULC Sensitive") +
  cowplot::theme_cowplot() +
  theme(legend.position = c(0.6, 0.8)) +
  theme(rect = element_rect(fill = "transparent"), 
        strip.background = element_rect(fill = "transparent"), 
        strip.text = element_blank()) +
  facet_wrap(~pretty) +
  # xlim(c(0, 34)) + 
  xlab("Clay (percent)")

@@

```{r re, fig.width=4.25}
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0,0,0), "cm")), 
                   rel_widths = c(1, 0.8)), 
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")),
ncol = 1, rel_heights = c(1, 0.05))
